Author: Chih-Hsuan (Carolyn) Kao;
Email: chkao831@stanford.edu;
Date: Nov 10th, 2019;
Title: STATS 240 HW2 Autumn19-20; 

Problem 3.5 part (a) 
Compute the sample mean mu and the sample covariance matrix of the log returns
```{r}
stock = read.table("m_logret_10stocks.txt", header = TRUE)
stock <- stock[2:length(stock)] #strip out date since unnecessary
stock <- stock[-c(157,158,159), ] #strip out blank last rows

sample_mu = colMeans(stock)
sample_mu
```

```{r}

sample_cov = cov(stock)
sample_cov
one_vec = matrix(1, ncol(stock), 1)
```
Problem 3.5 part (b)
Assume monthly target return is 0.3% and short selling is allowed (weight can be negative),
estimate the optimal portfolio weights
```{r}
#reference: Textbook page 70 formula
library(MASS)

A = t(sample_mu)%*%ginv(sample_cov)%*%one_vec
B = t(sample_mu)%*%ginv(sample_cov)%*%sample_mu
C = t(one_vec)%*%ginv(sample_cov)%*%one_vec
D = B%*%C - A%*%A

a = A[1,1]
b = B[1,1]
c = C[1,1]
d = D[1,1]

eff_weight = ( b*ginv(sample_cov)%*%one_vec - a*ginv(sample_cov)%*%sample_mu + 0.003*(c*ginv(sample_cov)%*%sample_mu - a*ginv(sample_cov)%*%one_vec) )/d
eff_weight #this is the optimal portfolio weight
```
Problem 3.5 part (c)
Using B=500 bootstrap samples for resampled weights from part (b)
```{r}
library(MASS)

calculate_weight <- function(data,term){
  
  dat <- data[term,]
  one_vec <- matrix(1, ncol(dat), 1)
  sample_mu = colMeans(dat)
  sample_cov = cov(dat)
  A = t(sample_mu)%*%ginv(sample_cov)%*%one_vec
  B = t(sample_mu)%*%ginv(sample_cov)%*%sample_mu
  C = t(one_vec)%*%ginv(sample_cov)%*%one_vec
  D = B%*%C - A%*%A

  a = A[1,1]
  b = B[1,1]
  c = C[1,1]
  d = D[1,1]

  eff_weight = ( b*ginv(sample_cov)%*%one_vec - a*ginv(sample_cov)%*%sample_mu + 0.003*(c*ginv(sample_cov)%*%sample_mu - a*ginv(sample_cov)%*%one_vec) )/d
  return(eff_weight)
}

library(boot)
#boot(object, f=function(object), R=Number of bootstrap samples)
boot_weight = boot(stock,calculate_weight,R=500)
#boot_weight
colMeans(boot_weight$t)

```
Problem 3.6 part (b)
Use bootstrap procedure to estimate standard errors of alpha, beta, Sharpe, and Treynor
```{r}
sp500ret = read.table("m_sp500ret_3mtcm.txt",
                   skip = 1,
                   sep="\t",
                   header = TRUE,
                   fill=FALSE, 
                   strip.white=TRUE)
sp500ret$X3mTCM <- sp500ret$X3mTCM/1200 #scale the risk free rate 
#compute the market risk premium (excess return of market)
sp500ret$risk_premium <- sp500ret$sp500 - sp500ret$X3mTCM

#this function returns vector contains alpha, beta, sharpe, treynor for each stock
calculate_ten <- function(data,term){
  
  dat <- data[term]
  
  Y = dat - sp500ret$X3mTCM #Y is stock premium
  CAPM = lm( Y~ sp500ret$risk_premium ) #stock premium~market premium
  alpha = CAPM$coefficients[1]
  beta = CAPM$coefficients[2]
  sharpe = mean(Y)/sd(Y)
  treynor = mean(Y)/beta
  
  vec = c(alpha,beta,sharpe,treynor)

  return(vec)
}

for (i in (1:10)){
  #boot(object, f=function(object), R=Number of bootstrap samples)
  boot_result = boot(stock[,i],calculate_ten,R=500)
  print(boot_result)
}
```
Problem 3.6 part (c) Test for each stock the null hypothesis alpha = 0
```{r}
stocklist <- list("AAPL","ADBE","ADP","AMD","DELL","GTW","HP","IBM","MSFT","ORCL")

for (i in (1:10)){
  Y = as.matrix(stock[,i])-sp500ret$X3mTCM
  X = sp500ret$risk_premium
  #Use linear regression on each stock
  model <- lm(Y~X)
  print(stocklist[[i]])
  cat("p value of alpha estimate:",summary(model)$coefficients[1,4])
  cat("\n")
  #perform hypothesis analysis at 95% confidence level
  if(summary(model)$coefficients[1,4] > 0.05){
    print("fail to reject null hypothesis that alpha is zero at 95% confidence level")
  } else {
    print("reject null hypothesis that alpha is zero at 95% confidence level")
  }
  cat("\n")
}
```
Problem 3.6 part (d) Use the regression model (3.24) to test null hypothesis alpha = 0
```{r}
Y = as.matrix(stock[,1:10]-sp500ret$X3mTCM)
X = sp500ret$risk_premium
model <- lm(Y~X)
alpha <- coef(model)[1,]
beta <- coef(model)[2,]
n <- dim(Y)[1]
q <- dim(Y)[2]
residual <- Y - alpha - X%*%t(beta)
V <- t(residual)%*%residual/n

Fval <- ((n-q-1)/q)*alpha%*%ginv(V)%*%alpha/(1+mean(X)^2/mean((X-mean(X))^2))
cat("F-value is ",Fval)

lower_CI <- qf(0.025,q,n-q-1)
upper_CI <- qf(0.975,q,n-q-1)

cat("\n")
cat(" lower CI is: ",lower_CI)
cat(" upper CI is: ",upper_CI)
cat("\n")
cat("F value lies between CI, so we fail to reject the null hypothesis that alpha equals zero at 95% confidence level using the regression model (3.24)")
```



